\thesistitle

### 2019-07-25 sections/introduction.tex
AAH

\section{Contributions}
\todo{TODO}
%Our research makes the following contributions:
%\begin{enumerate}
%	\item We deliver several novel measurements regarding code clones on a large corpus of Java projects.
%	\item We deliver a novel clone detection tool that finds refactorable clones in Java.
%	\item We deliver a novel clone refactoring tool that suggests refactorings to be applied, and applies these refactorings.
%	\item We give further recommendations in how refactoring can be automatically applied to improve maintainability in software projects.
%\end{enumerate}

@@

\section{Outline}
\todo{Rewrite this part}
In Chapter~\ref{ch:background} we describe the background of this thesis. In Chapter~\ref{chap:clonetypes} we list shortcomings with clone definitions from literature and propose a set of clone type definitions which can be automatically refactored. In Chapter \ref{ch:clonerefactor} we propose a tool to detect, analyze and automatically refactor such clones that can be refactored. Using this tool we perform a set of experiments, of which the results are shown in Chapter~\ref{ch:results} and discussed in Chapter~\ref{ch:discussion}. Chapter~\ref{ch:related_work} contains the work related to this thesis. Finally, we present our concluding remarks in Chapter~\ref{ch:conclusion} together with future work.

>>>>

\section{Contributions}
Many modern clone detection techniques and thresholds have been validated by manually assessing a sample of the results \cite{sajnani2016sourcerercc, cordy2011nicad, jiang2007deckard}. 
%Our research makes the following contributions:
%\begin{enumerate}
%	\item We deliver several novel measurements regarding code clones on a large corpus of Java projects.
%	\item We deliver a novel clone detection tool that finds refactorable clones in Java.
%	\item We deliver a novel clone refactoring tool that suggests refactorings to be applied, and applies these refactorings.
%	\item We give further recommendations in how refactoring can be automatically applied to improve maintainability in software projects.
%\end{enumerate}

@@

\section{Outline}
In Chapter~\ref{ch:background} we describe the background of this thesis. In Chapter~\ref{chap:clonetypes} we list shortcomings with clone definitions from literature and propose a set of clone type definitions which can be automatically refactored. In Chapter \ref{ch:clonerefactor} we propose a tool to detect, analyze and automatically refactor such clones that can be refactored. Using this tool we perform a set of experiments, of which the results are shown in Chapter~\ref{ch:results} and discussed in Chapter~\ref{ch:discussion}. Chapter~\ref{ch:related_work} contains the work related to this thesis. Finally, we present our concluding remarks in Chapter~\ref{ch:conclusion} together with future work.
